---
title: "2021 MLB Sprint Performance Normative Values"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: 
      version: 4
      bg: "#2C82B5"
      fg: "#101010"
      primary: "#682C37"
      navbar-bg: "#2C82B5" #blue
      base_font:
        google: Space Grotesk
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(plotly)
sprints <- read.csv("running_splits 2021 min 10.csv")

df <- sprints %>% 
   mutate(t30 = seconds_since_hit_030) %>% 
   mutate(t60 = seconds_since_hit_060-seconds_since_hit_030) %>% 
   mutate(t90 = seconds_since_hit_090-seconds_since_hit_060) %>% 
   mutate(total90 = seconds_since_hit_090)

#getting percentiles
dfx <- as.data.frame(apply(df[28:31] , 2 , quantile , probs = seq(0,1,0.05) , na.rm = TRUE ))
dfx$Percentile <- row.names(dfx)
dfx$Percentile<-as.numeric(gsub("\\%","",dfx$Percentile))
dfx$Percentile <- 100-dfx$Percentile
rownames(dfx)<-NULL
dfx<-round(dfx,2)
colnames(dfx) <- c("Time 0 to 30 ft", "Time 30 to 60 ft", " Time 60 to 90 ft", "Total Time (0 to 90 ft)", "Percentile")
#plot fxn
time_percentileplotter <- function(x){
ggplot(dfx, aes(Percentile,x)) +
  geom_point() +geom_smooth(color='#2C82B5') + theme_minimal() 
}
```

# All Positions 

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------


### Total time 0 to 90 ft

```{r}
p <- time_percentileplotter(dfx$`Total Time (0 to 90 ft)`) + labs(y="Total Time (0 to 90 ft)")
ggplotly(p)
```

### Time 0 to 30 ft
```{r}
p <- time_percentileplotter(dfx$`Time 0 to 30 ft`) + labs(y="Time 0 to 30 ft")
ggplotly(p)
```

### Time 30 to 60 ft
```{r}
p <- time_percentileplotter(dfx$`Time 30 to 60 ft`) + labs(y="Time 30 to 60 ft")
ggplotly(p)
```

### Time 60 to 90 ft

```{r}
p <- time_percentileplotter(dfx$` Time 60 to 90 ft`) + labs(y="Time 60 to 90 ft")
ggplotly(p)
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Total time 0 to 90 ft

```{r}
dfz <- dfx %>% 
  select(`Total Time (0 to 90 ft)`,Percentile)
knitr::kable(dfz)
```

### Time 0 to 30 ft

```{r}
dfz<- dfx %>% 
  select(`Time 0 to 30 ft`, Percentile)
knitr::kable(dfz)
```


### Time 30 to 60 ft

```{r}
dfz<- dfx %>% 
  select(`Time 30 to 60 ft`, Percentile)
knitr::kable(dfz)
```

### Time 60 to 90 ft

```{r}
dfz<- dfx %>% 
  select(` Time 60 to 90 ft`, Percentile)
knitr::kable(dfz)
```

# Outfielders

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

```{r}
dfx <- df %>% 
  filter(position_name == "RF" | position_name == "CF" | position_name == "LF" )

dfx <- as.data.frame(apply(dfx[28:31] , 2 , quantile , probs = seq(0,1,0.05) , na.rm = TRUE ))
dfx$Percentile <- row.names(dfx)
dfx$Percentile<-as.numeric(gsub("\\%","",dfx$Percentile))
dfx$Percentile <- 100-dfx$Percentile
rownames(dfx)<-NULL
dfx<-round(dfx,2)
colnames(dfx) <- c("Time 0 to 30 ft", "Time 30 to 60 ft", " Time 60 to 90 ft", "Total Time (0 to 90 ft)", "Percentile")
```

### Total time 0 to 90 ft

```{r}
p <- time_percentileplotter(dfx$`Total Time (0 to 90 ft)`) + labs(y="Total Time (0 to 90 ft)")
ggplotly(p)
```

### Time 0 to 30 ft
```{r}
p <- time_percentileplotter(dfx$`Time 0 to 30 ft`) + labs(y="Time 0 to 30 ft")
ggplotly(p)
```

### Time 30 to 60 ft
```{r}
p <- time_percentileplotter(dfx$`Time 30 to 60 ft`) + labs(y="Time 30 to 60 ft")
ggplotly(p)
```

### Time 60 to 90 ft

```{r}
p <- time_percentileplotter(dfx$` Time 60 to 90 ft`) + labs(y="Time 60 to 90 ft")
ggplotly(p)
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Total time 0 to 90 ft

```{r}
dfz <- dfx %>% 
  select(`Total Time (0 to 90 ft)`,Percentile)
knitr::kable(dfz)
```

### Time 0 to 30 ft

```{r}
dfz<- dfx %>% 
  select(`Time 0 to 30 ft`, Percentile)
knitr::kable(dfz)
```


### Time 30 to 60 ft

```{r}
dfz<- dfx %>% 
  select(`Time 30 to 60 ft`, Percentile)
knitr::kable(dfz)
```

### Time 60 to 90 ft

```{r}
dfz<- dfx %>% 
  select(` Time 60 to 90 ft`, Percentile)
knitr::kable(dfz)
```


# Middle Infielders

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

```{r}
dfx <- df %>% 
  filter(position_name == "SS" | position_name == "2B" )

dfx <- as.data.frame(apply(dfx[28:31] , 2 , quantile , probs = seq(0,1,0.05) , na.rm = TRUE ))
dfx$Percentile <- row.names(dfx)
dfx$Percentile<-as.numeric(gsub("\\%","",dfx$Percentile))
dfx$Percentile <- 100-dfx$Percentile
rownames(dfx)<-NULL
dfx<-round(dfx,2)
colnames(dfx) <- c("Time 0 to 30 ft", "Time 30 to 60 ft", " Time 60 to 90 ft", "Total Time (0 to 90 ft)", "Percentile")
```

### Total time 0 to 90 ft

```{r}
p <- time_percentileplotter(dfx$`Total Time (0 to 90 ft)`) + labs(y="Total Time (0 to 90 ft)")
ggplotly(p)
```

### Time 0 to 30 ft
```{r}
p <- time_percentileplotter(dfx$`Time 0 to 30 ft`) + labs(y="Time 0 to 30 ft")
ggplotly(p)
```

### Time 30 to 60 ft
```{r}
p <- time_percentileplotter(dfx$`Time 30 to 60 ft`) + labs(y="Time 30 to 60 ft")
ggplotly(p)
```

### Time 60 to 90 ft

```{r}
p <- time_percentileplotter(dfx$` Time 60 to 90 ft`) + labs(y="Time 60 to 90 ft")
ggplotly(p)
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Total time 0 to 90 ft

```{r}
dfz <- dfx %>% 
  select(`Total Time (0 to 90 ft)`,Percentile)
knitr::kable(dfz)
```

### Time 0 to 30 ft

```{r}
dfz<- dfx %>% 
  select(`Time 0 to 30 ft`, Percentile)
knitr::kable(dfz)
```


### Time 30 to 60 ft

```{r}
dfz<- dfx %>% 
  select(`Time 30 to 60 ft`, Percentile)
knitr::kable(dfz)
```

### Time 60 to 90 ft

```{r}
dfz<- dfx %>% 
  select(` Time 60 to 90 ft`, Percentile)
knitr::kable(dfz)
```


# Corner Infielders

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

```{r}
dfx <- df %>% 
  filter(position_name == "1B" | position_name == "3B")

dfx <- as.data.frame(apply(dfx[28:31] , 2 , quantile , probs = seq(0,1,0.05) , na.rm = TRUE ))
dfx$Percentile <- row.names(dfx)
dfx$Percentile<-as.numeric(gsub("\\%","",dfx$Percentile))
dfx$Percentile <- 100-dfx$Percentile
rownames(dfx)<-NULL
dfx<-round(dfx,2)
colnames(dfx) <- c("Time 0 to 30 ft", "Time 30 to 60 ft", " Time 60 to 90 ft", "Total Time (0 to 90 ft)", "Percentile")
```

### Total time 0 to 90 ft

```{r}
p <- time_percentileplotter(dfx$`Total Time (0 to 90 ft)`) + labs(y="Total Time (0 to 90 ft)")
ggplotly(p)
```

### Time 0 to 30 ft
```{r}
p <- time_percentileplotter(dfx$`Time 0 to 30 ft`) + labs(y="Time 0 to 30 ft")
ggplotly(p)
```

### Time 30 to 60 ft
```{r}
p <- time_percentileplotter(dfx$`Time 30 to 60 ft`) + labs(y="Time 30 to 60 ft")
ggplotly(p)
```

### Time 60 to 90 ft

```{r}
p <- time_percentileplotter(dfx$` Time 60 to 90 ft`) + labs(y="Time 60 to 90 ft")
ggplotly(p)
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Total time 0 to 90 ft

```{r}
dfz <- dfx %>% 
  select(`Total Time (0 to 90 ft)`,Percentile)
knitr::kable(dfz)
```

### Time 0 to 30 ft

```{r}
dfz<- dfx %>% 
  select(`Time 0 to 30 ft`, Percentile)
knitr::kable(dfz)
```


### Time 30 to 60 ft

```{r}
dfz<- dfx %>% 
  select(`Time 30 to 60 ft`, Percentile)
knitr::kable(dfz)
```

### Time 60 to 90 ft

```{r}
dfz<- dfx %>% 
  select(` Time 60 to 90 ft`, Percentile)
knitr::kable(dfz)
```


# Catchers

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

```{r}
dfx <- df %>% 
  filter(position_name == "C")

dfx <- as.data.frame(apply(dfx[28:31] , 2 , quantile , probs = seq(0,1,0.05) , na.rm = TRUE ))
dfx$Percentile <- row.names(dfx)
dfx$Percentile<-as.numeric(gsub("\\%","",dfx$Percentile))
dfx$Percentile <- 100-dfx$Percentile
rownames(dfx)<-NULL
dfx<-round(dfx,2)
colnames(dfx) <- c("Time 0 to 30 ft", "Time 30 to 60 ft", " Time 60 to 90 ft", "Total Time (0 to 90 ft)", "Percentile")
```

### Total time 0 to 90 ft

```{r}
p <- time_percentileplotter(dfx$`Total Time (0 to 90 ft)`) + labs(y="Total Time (0 to 90 ft)")
ggplotly(p)
```

### Time 0 to 30 ft
```{r}
p <- time_percentileplotter(dfx$`Time 0 to 30 ft`) + labs(y="Time 0 to 30 ft")
ggplotly(p)
```

### Time 30 to 60 ft
```{r}
p <- time_percentileplotter(dfx$`Time 30 to 60 ft`) + labs(y="Time 30 to 60 ft")
ggplotly(p)
```

### Time 60 to 90 ft

```{r}
p <- time_percentileplotter(dfx$` Time 60 to 90 ft`) + labs(y="Time 60 to 90 ft")
ggplotly(p)
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Total time 0 to 90 ft

```{r}
dfz <- dfx %>% 
  select(`Total Time (0 to 90 ft)`,Percentile)
knitr::kable(dfz)
```

### Time 0 to 30 ft

```{r}
dfz<- dfx %>% 
  select(`Time 0 to 30 ft`, Percentile)
knitr::kable(dfz)
```


### Time 30 to 60 ft

```{r}
dfz<- dfx %>% 
  select(`Time 30 to 60 ft`, Percentile)
knitr::kable(dfz)
```

### Time 60 to 90 ft

```{r}
dfz<- dfx %>% 
  select(` Time 60 to 90 ft`, Percentile)
knitr::kable(dfz)
```

